---
title: "Project3"
author: "Raj Pawar"
date: "`r Sys.Date()`"
output: html_document
---

### Clear memory
```{r}
rm(list=ls())
```

```{r}
library(readr)
library(leaps)
library(bestglm)
library(ggplot2)
library(broom)
library(MASS)
```

### Tasks 1: Data preparation
```{r}
bodymeasurements <- read_csv("bodymeasurements.csv", TRUE)
#View(bodymeasurements)
```

```{r}
summary(bodymeasurements)
bodymeasurements <- as.data.frame(bodymeasurements)
#bodymeasurements
```

# Check for missing values
```{r}
sum(is.na(bodymeasurements)) 
#0 missing values
```

```{r}
drops <- c("ID")
bodymeasurements <- bodymeasurements[ , !(names(bodymeasurements) %in% drops)]
```

```{r}
#bodymeasurements$Weight <- bodymeasurements$Weight/100
#summary(bodymeasurements)
```

```{r}
fit_model <- lm(Height ~ Chest+Age+Sex+Belly+Thigh+Knee+Calf+Ankle+Biceps+Wrist+Weight ,data=bodymeasurements)
summary(fit_model)
```

```{r}
fit_model_res <- augment(fit_model)
summary(fit_model_res)
```

```{r}
ggplot(fit_model_res, aes(x = .fitted, y =.resid))+geom_point()+ geom_hline(yintercept = 0)+
  xlab('Fitted values')+ylab('Residuals')+theme(axis.text=element_text(size=16), axis.title=element_text(size=16), plot.title = element_text(hjust = 0.5)) + ggtitle('Residuals vs Fitted: Price')
```

# Q-Q plot
```{r}
ggplot(data = fit_model_res, aes(sample= .std.resid)) +stat_qq() + stat_qq_line(col = 'red')+ylab('Standardized residuals')+xlab('Theoretical Quantiles')+ggtitle('Normal Q-Q: Height')+
  theme(axis.text=element_text(size=16), axis.title=element_text(size=16), plot.title = element_text(hjust = 0.5))
```


##Question2
# Make categorical variables as factors

```{r}
#models <- regsubsets(Height~., data = bodymeasurements, nvmax = NULL)
#summary(models)

#x <- summary(models)
#which.max(x$adjr2)
#x$which[8,]
```

```{r}
library(olsrr)
fullmodel <- lm(Height ~ ., data = bodymeasurements)
ols_step_best_subset(fullmodel)
View(ols_step_best_subset(fullmodel))
#step_model <- stepAIC(fit_model, direction= "both")
```

```{r}
bodymeasurements$Sex <- as.factor(bodymeasurements$Sex)
```

```{r}
bodymeasurements_subset <- bodymeasurements[!(names(bodymeasurements) %in% c("Knee", "Ankle", "Age"))] 
```

```{r}
col_order <- c("Sex", "Chest", "Belly" , "Thigh" , "Calf" , "Biceps" , "Wrist" , "Weight", "Height")
bodymeasurements_subset <- bodymeasurements_subset[, col_order]
summary(bodymeasurements_subset)
```

#model6 for BIC
```{r}
#best_subsets_BIC %>% filter(BIC == min(ols_step_best_subset$))
```

#model8 for AIC

```{r}
modelFull <- lm(Height ~ ., data = bodymeasurements_subset) #model with all variables
summary(modelFull)
```

# Best explanatory variables using BIC
```{r}
#bestglm(bodymeasurements_subset, IC = "BIC") # outputs the set
```

```{r}
model1 <- lm(Height ~  Sex + Belly + Thigh + Calf + Biceps + Weight, data = bodymeasurements_subset)
```

# Best explanatory variables using AIC
```{r}
#bestglm(bodymeasurements_subset, IC = "AIC")

model2 <- lm(Height ~  Chest + Sex + Belly + Thigh + Calf + Biceps + Wrist +
               Weight, data = bodymeasurements_subset)

```

# Verify the models created from the subset selections
```{r}
AIC(modelFull, model1, model2) # 
BIC(modelFull, model1, model2) # 
```

#2-3. Estimate the "best?" linear model for the dependent variable w.r.t. the BIC from ii.

# through BIC(); model1 is the best linear model
```{r}
summary(model1)
```

# Assumptions to check for the BIC Model
```{r}
model1_res = augment(model1)
```

# Residuals vs fitted plot
```{r}
ggplot(model1_res, aes(x = .fitted, y =.resid))+geom_point()+ geom_hline(yintercept = 0)+
  xlab('Fitted values')+ylab('Residuals')+theme(axis.text=element_text(size=16), axis.title=element_text(size=16), plot.title = element_text(hjust = 0.5)) + ggtitle('Residuals vs Fitted') +  labs(subtitle = "Estimating through best BIC model")
```

# Q-Q plot
```{r}
ggplot(data = model1_res, aes(sample= .std.resid)) +stat_qq() + stat_qq_line(col = 'red')+ylab('Standardized residuals')+xlab('Theoretical Quantiles')+ggtitle('Normal Q-Q')+
  theme(axis.text=element_text(size=16), axis.title=element_text(size=16), plot.title = element_text(hjust = 0.5)) + labs(subtitle = "Estimating through best BIC model")
```

# estimating 95% confidence interval for estimated regression coefficients
```{r}
confint(model1, level = 0.95) # estimating confidence interval for estimated regression coefficients
round(confint(model1, level = 0.95), 2)
```

#goodness of fit: R2
```{r}
R2 <- summary(model1)[["r.squared"]]
R2
```
